A New Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-07-08 analysis/article.Rmd
fix: change center to Leipzig

  **Methods**:
      We retrospectively analysed clinical and laboratory data of 654 patients who were recruited during the evaluation process for liver transplantation at the University Hospital Greifswald.
      After comparing 13 different ML algorithms in a nested cross-validation setting and selecting the best performing one we build a new model to predict 90-day mortality in patients with end-stage liver disease.

>>>>

  **Methods**:
      We retrospectively analysed clinical and laboratory data of 654 patients who were recruited during the evaluation process for liver transplantation at the University Hospital Leipzig.
      After comparing 13 different ML algorithms in a nested cross-validation setting and selecting the best performing one we build a new model to predict 90-day mortality in patients with end-stage liver disease.
